Spfy: distributed predictive genomics of E.coli with graph based result linkage

### 2017-08-17 paper-webserver.tex
ADD: 3rd intro para to implementation

>>>>

% para: intro to the spfy stack
Spfy's server-side code is developed in Python and the website served to users is developed using the React JavaScript library.
When users upload genomes for analysis: (i) they first make the upload through the ReactJS-based website. 
The public web service accepts up to 200 MB of genome files (50 genomes compressed, or 120 genomes compressed).
(ii) When files are uploaded, the user-selected analysis options are enqueued into the Redis Queue \url{http://python-rq.org/} task queue.
Redis Queue consists of a Redis Database \url{https://redis.io/} and task queue workers which run as Python processes.
(iii) The workers dequeue the various analyses and run them in parallel and results are stored back in the Redis database.
(iv) Python functions are then used to parse the results and permanently store them in Blazegraph \url{https://www.blazegraph.com/} - a graph database.
The entire Spfy platform is packaged as a series of Docker \url{https://www.docker.com/} containers and orchestrated using Docker Compose \url{https://docs.docker.com/compose/}.
